### 2019-07-26 paper/paper.tex
Update paper.tex

As for the memory setup, there are also alternative methodologies. First, it's necessary to choose among Static vs. Dynamic memory allocations \citeprajapati2015}. To improve speed-up, Static "once-and-for-all" allocations are often preferred (even at a cost of higher average memory utilization). Second, shared-memory strategies must be determined. Depending on both object-size and CPU architecture -cache size and its distribution among cores-, it could be optimal to use large shared arrays or -alternatively- smaller core-specific objects. Splitting output matrices to work with smaller non-shared arrays could be useful for cache optimization purposes, but it could also entail additional communication costs and higher memory requirements \cite{ahmed2015}. In practice, feature selection algorithms usually prefer shared-arrays for high performance computing. \vskip 6pt

@@

>>>>

As for the memory setup, there are also alternative methodologies. First, it's necessary to choose among Static vs. Dynamic memory allocations \cite{prajapati2015}. To improve speed-up, Static "once-and-for-all" allocations are often preferred (even at a cost of higher average memory utilization). Second, shared-memory strategies must be determined. Depending on both object-size and CPU architecture -cache size and its distribution among cores-, it could be optimal to use large shared arrays or -alternatively- smaller core-specific objects. Splitting output matrices to work with smaller non-shared arrays could be useful for cache optimization purposes, but it could also entail additional communication costs and higher memory requirements \cite{ahmed2015}. In practice, feature selection algorithms usually prefer shared-arrays for high performance computing. \vskip 6pt

@@

\subsection{OLS estimation}
\label{subsub:ols}
Efficient Ordinary Least Squares (OLS) algorithms rely on Linear Algebra operations (matrix decomposition, matrix inversion, etc.).\footnote{Optimization alternatives (i.e. Gradient descent), while quite inefficient for linear models, can also be used for non-linear estimations \cite{abdi2007}} The traditional $(X'X)^{-1}$ operation could be time-expensive with unstable solutions under certain conditions \cite{jameson1981}. A preferred method is the QR-decomposition developed by Francis \cite{francis1961} and Kublanovskaya \cite{kublanovskaya1962s}. The QR factorization allows us to decompose any full rank $N \times p$ matrix $\bar{X}$ as:

\begin{equation}
    X=QR
\end{equation}

where

\begin{itemize}
    \item[•] $Q$ is a $N \times p$ matrix with $Q'Q=I$  ; and
    \item[•] $R$ a $p \times p$ upper triangular matrix.
\end{itemize}

The QR decomposition is fast and provides stable numerical solutions under rank-deficient matrices. Alternative factorizations are either slower (SVD decomposition) or potentially unstable (Cholesky decomposition)\cite{agarwal2014}. \vskip 6pt

\verb GlobalSearchRegression.jl  OLS estimation through QR-decompositions outperform existing Julia alternatives (like \verb GLM.jl)  allowing for large speed-ups compared with \verb R-lm    and \verb Stata-regress  commands. Table 3 shows execution time differences for a 200 covariates - 1000 observations - multivariate linear regression \footnote{Execution times were calculated for alternative OLS algorithms available for all-subset-regression packages in Julia,  %and Stata.}.
\vskip 6pt

It must be notice that execution times are compilation-free, because all-subset-regression algorithms must perform thousand to millions of regressions where compilation time is absent (it only affects the first regression).
\vskip 6pt
